new_analses

### 2021-06-23 Frontiers/Frontiers.Rmd
gh

---
title: "Adaptation of Palmer amaranth to the upper Midwest United States"
runtitle: "Short Title"
documentclass: frontiersSCNS  # or frontiersHLTH, or frontiersFPHY
author:
  - name: Maxwel Coura Oliveira
    affiliation: '1'
    etal: Oliveira # First author's last name. 
  - name: Amit J Jhala
    affiliation: '2'
  - name: Mark Bernards
    affiliation: '3'
  - name: Strahinja Stephanovic
    affiliation: '4'
  - name: Chris Proctor
    affiliation: '2'
  - name: Rodrigo Werle
    affiliation: '1'
    email: rwerle@wisc.edu # Indicates corresponding Author
    institution: Laboratory X, Institute X, Department of Agronomy and Horticulture, University of Wisconsin-Madison
    street: 1575 Linden Drive
    city: Madison
    state: Wisconsin # only USA, Australia, Canada
    zip: 53706
    country: United States of America
affiliation:
  - id: '1'
    department: Department of Agronomy
    institution: University of Wisconsin-Madison
    city: Madison
    state: Wisconsin # only USA, Australia, Canada
    country: United States of America
  - id: '2' 
    department: Department of Agronomy and Horticulture
    institution: University of Nebraska-Lincoln
    city: Lincoln
    state: Nebraska # only USA, Australia, Canada
    country: United States of America
  - id: '3' 
    department: Department X
    institution: Western Illinois University
    city: Macomb
    state: Illinois # only USA, Australia, Canada
    country: United States of America
  - id: '4' 
    department: Department of Agronomy and Horticulture
    institution: University of Nebraska-Lincoln
    city: Grant
    state: Nebraska # only USA, Australia, Canada
    country: United States of America

output: rticles::frontiers_article
csl: frontiers.csl
bibliography: test.bib
---

@@

%All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\tiny
 \keyFont{ \section{Keywords:} Text Text Text Text Text Text Text Text }

@@

>>>>

---
title: "Adaptation of Palmer amaranth to the upper Midwest"
runtitle: "Short Title"
documentclass: frontiersSCNS  # or frontiersHLTH, or frontiersFPHY
author:
  - name: Maxwel C Oliveira
    affiliation: '1'
    etal: Oliveira # First author's last name. 
  - name: Amit J Jhala
    affiliation: '2'
  - name: Mark Bernards
    affiliation: '3'
  - name: Chris Proctor
    affiliation: '2'
  - name: Strahinja Stepanovic
    affiliation: '2'
  - name: Rodrigo Werle
    affiliation: '1'
    email: rwerle@uwisc.edu # Indicates corresponding Author
    institution: Department of Agronomy, University of Wisconsin-Madison, United States
    street: 1575 Linden Dr
    city: Madison
    state: Wisconsin # only USA, Australia, Canada
    zip: 53705
    country: United States
affiliation:
  - id: '1'
    department: Department of Agronomy
    institution: University of Wisconsin-Madison
    city: Madison
    state: Wisconsin # only USA, Australia, Canada
    country: United States
  - id: '2' 
    department: Department of Agronomy and Horticulture
    institution: University of Nebraska-Lincoln
    city: Lincoln
    state: Nebraska # only USA, Australia, Canada
    country: United States
  - id: '3' 
    department: Department of Agronomy
    institution: Western Illinois University
    city: Macomb
    state: Illnois # only USA, Australia, Canada
    country: United States
output: rticles::frontiers_article
csl: frontiers.csl
bibliography: test.bib
---

@@

%All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\tiny
 \keyFont{ \section{Keywords:} Text Text Text Text Text Text Evolution Weed }

@@

# Material and Methods {-}

## Plant material {-}

The study was performed with a *A. palmeri* accession (Per1) from Perkins County, Nebraska. Per1 accession collection is documented in [], with no  confirmed herbicide resistance.

### 2021-06-23 Frontiers/Frontiers.tex
gh

@@

\def\Authors{
  Maxwel Coura Oliveira\,\textsuperscript{1},
  Amit J Jhala\,\textsuperscript{2},
  Mark Bernards\,\textsuperscript{3},
  Strahinja Stephanovic\,\textsuperscript{4},
  Chris Proctor\,\textsuperscript{2},
  Rodrigo Werle\,\textsuperscript{1*}}

@@

  \textsuperscript{1} Department of Agronomy, University of Wisconsin-Madison,  Madison,  Wisconsin,  United States of America

  \textsuperscript{2} Department of Agronomy and Horticulture, University of Nebraska-Lincoln,  Lincoln,  Nebraska,  United States of America

  \textsuperscript{3} Department X, Western Illinois University,  Macomb,  Illinois,  United States of America

  \textsuperscript{4} Department of Agronomy and Horticulture, University of Nebraska-Lincoln,  Grant,  Nebraska,  United States of America
  }

@@

  \def\corrAuthor{Rodrigo Werle}\def\corrAddress{Laboratory X, Institute X, Department of Agronomy and Horticulture,
University of Wisconsin-Madison\\1575 Linden Drive\\Madison, Wisconsin, 53706 United States of America}\def\corrEmail{\href{mailto:rwerle@wisc.edu}{\nolinkurl{rwerle@wisc.edu}}}

@@

\title[Short Title]{Adaptation of Palmer amaranth to the upper Midwest United States}
\author[\firstAuthorLast]{\Authors}
\address{} %This field will be automatically populated
\correspondance{} %This field will be automatically populated

@@

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{x <-}\StringTok{ }\DecValTok{0}\OperatorTok{:}\DecValTok{100}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{999}\NormalTok{)}
\NormalTok{y <-}\StringTok{ }\DecValTok{2} \OperatorTok{*}\StringTok{ }\NormalTok{(x }\OperatorTok{+}\StringTok{ }\KeywordTok{rnorm}\NormalTok{(}\KeywordTok{length}\NormalTok{(x), }\DataTypeTok{sd =} \DecValTok{3}\NormalTok{) }\OperatorTok{+}\StringTok{ }\DecValTok{3}\NormalTok{)}
\KeywordTok{plot}\NormalTok{(x, y)}
\end{Highlighting}
\end{Shaded}

@@

{\centering \includegraphics[width=85mm,height=85mm]{Adaptation_files/figure-latex/Figure-1-1}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Neurobot2013}{}%
Author4, N., and Author5, N. (2013). Title of the article.
\emph{Frontiers in Neurorobotics} 7.
doi:\href{https://doi.org/10.3389/fnbot.2013.56789}{10.3389/fnbot.2013.56789}.

@@

>>>>

% Pandoc citation processing
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for calculating minipage widths
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\def\Authors{
  Maxwel C Oliveira\,\textsuperscript{1},
  Amit J Jhala\,\textsuperscript{2},
  Mark Bernards\,\textsuperscript{3},
  Chris Proctor\,\textsuperscript{2},
  Strahinja Stepanovic\,\textsuperscript{2},
  Rodrigo Werle\,\textsuperscript{1*}}

@@

  \textsuperscript{1} Department of Agronomy, University of
Wisconsin-Madison,  Madison,  Wisconsin,  United States

  \textsuperscript{2} Department of Agronomy and
Horticulture, University of
Nebraska-Lincoln,  Lincoln,  Nebraska,  United States

  \textsuperscript{3} Department of Agronomy, Western Illinois
University,  Macomb,  Illnois,  United States
  }

@@

  \def\corrAuthor{Rodrigo Werle}\def\corrAddress{Department of Agronomy,
University of Wisconsin-Madison, United States\\1575 Linden
Dr\\Madison, Wisconsin, 53705 United
States}\def\corrEmail{\href{mailto:rwerle@uwisc.edu}{\nolinkurl{rwerle@uwisc.edu}}}

@@

\title[Short Title]{Adaptation of Palmer amaranth to the upper Midwest}
\author[\firstAuthorLast]{\Authors}
\address{} %This field will be automatically populated
\correspondance{} %This field will be automatically populated

@@

\hypertarget{material-and-methods}{%
\section*{Material and Methods}\label{material-and-methods}}
\addcontentsline{toc}{section}{Material and Methods}

\hypertarget{plant-material}{%
\subsection*{Plant material}\label{plant-material}}
\addcontentsline{toc}{subsection}{Plant material}

The study was performed with a \emph{A. palmeri} accession (Per1) from
Perkins County, Nebraska. The accession Per1 was documented as
glyphosate-susceptible {[}{]}.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{x }\OtherTok{\textless{}{-}} \DecValTok{0}\SpecialCharTok{:}\DecValTok{100}
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{999}\NormalTok{)}
\NormalTok{y }\OtherTok{\textless{}{-}} \DecValTok{2} \SpecialCharTok{*}\NormalTok{ (x }\SpecialCharTok{+} \FunctionTok{rnorm}\NormalTok{(}\FunctionTok{length}\NormalTok{(x), }\AttributeTok{sd =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+} \DecValTok{3}\NormalTok{)}
\FunctionTok{plot}\NormalTok{(x, y)}
\end{Highlighting}
\end{Shaded}

@@

{\centering \includegraphics[width=85mm,height=85mm]{Frontiers_files/figure-latex/Figure-1-1}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Neurobot2013}{}%
Author4, N., and Author5, N. (2013). Title of the article.
\emph{Frontiers in Neurorobotics} 7.
doi:\href{https://doi.org/10.3389/fnbot.2013.56789}{10.3389/fnbot.2013.56789}.

@@

\end{CSLReferences}

### 2021-06-23 new_analyses.Rmd
s
gh

>>>>

#### -----

```{r}
library(ggdist)
library(PupillometryR)
```

# Biomass

```{r}
data %>% 
  rename(month = planting,
         planting = planting_1) %>% 
  mutate(planting = mdy(planting),
         harvest = mdy(harvest),
         doyp = yday(planting)) %>% 
  mutate_if(is_character, as_factor) -> data1
```

```{r}
data1 %>% 
  mutate(month = fct_recode(month,
                            "first planting" = "June",
                            "second planting" = "July")) -> data1
```

```{r}
data1 %>% 
  mutate(location = str_to_title(location)) %>% 
  filter(crop == "corn") %>% 
  filter(!is.na(weight)) %>% 
  ggplot(aes(x = fct_reorder(location, weight), y = weight,
             color = location, 
             fill = location)) + 
  geom_jitter(position = position_nudge(x = -0.2, y = 0), alpha = 0.1) +
  geom_boxplot(width = 0.2, outlier.shape = NA, alpha = 0.5) +
  geom_flat_violin(position = position_nudge(x = 0.2, y = 0), 
                   stat = "ydensity",
                   alpha = 0.8, scale = "count") +
  stat_summary(fun = "mean", colour = "red", size = 1, geom = "point") +
  scale_color_viridis_d(option = "H") + 
  scale_fill_viridis_d(option = "H") + 
  theme_test() +
  facet_grid(month ~ crop, scales = "free") +
  coord_flip() +
  labs(x = NULL, y = NULL) +
  theme(legend.position = "none",
        strip.text = element_markdown(face = "bold")) -> fg1
```

```{r}
data1 %>% 
  mutate(location = str_to_title(location)) %>% 
  filter(crop == "fallow") %>% 
  filter(!is.na(weight)) %>% 
  ggplot(aes(x = fct_reorder(location, weight), y = weight,
             color = location, 
             fill = location)) + 
  geom_jitter(position = position_nudge(x = -0.2, y = 0), alpha = 0.1) +
  geom_boxplot(width = 0.2, outlier.shape = NA, alpha = 0.5) +
  geom_flat_violin(position = position_nudge(x = 0.2, y = 0), 
                   stat = "ydensity",
                   alpha = 0.8, scale = "count") +
  stat_summary(fun = "mean", colour = "red", size = 1, geom = "point") +
  scale_color_viridis_d(option = "H") + 
  scale_fill_viridis_d(option = "H") + 
  theme_test() +
  facet_grid(month ~ crop, scales = "free") +
  coord_flip() +
  labs(x = NULL, y = "Biomass (g)") +
  theme(legend.position = "none",
        strip.text = element_markdown(face = "bold")) -> fg2
```

```{r}
data1 %>% 
  mutate(location = str_to_title(location)) %>% 
  filter(crop == "soybean") %>% 
  filter(!is.na(weight)) %>% 
  ggplot(aes(x = fct_reorder(location, weight), y = weight,
             color = location, 
             fill = location)) + 
  geom_jitter(position = position_nudge(x = -0.2, y = 0), alpha = 0.1) +
  geom_boxplot(width = 0.2, outlier.shape = NA, alpha = 0.5) +
  geom_flat_violin(position = position_nudge(x = 0.2, y = 0), 
                   stat = "ydensity",
                   alpha = 0.8, scale = "count") +
  stat_summary(fun = "mean", colour = "red", size = 1, geom = "point") +
  scale_color_viridis_d(option = "H") + 
  scale_fill_viridis_d(option = "H") + 
  theme_test() +
  facet_grid(month ~ crop, scales = "free") +
  coord_flip() +
  labs(x = NULL, y = NULL) +
  theme(legend.position = "none",
        strip.text = element_markdown(face = "bold")) -> fg3
```

```{r}
f4 <- fg1 | fg2 | fg3 +
  plot_annotation(
  title = NULL) 
  ggsave("biomass.png", width = 9, height = 5, dpi = 600, f4)
```

# Height

```{r}
data1 %>% 
  mutate(location = str_to_title(location)) %>% 
  filter(crop == "corn") %>% 
  filter(!is.na(height)) %>% 
  ggplot(aes(x = fct_reorder(location, height), y = height,
             color = location, 
             fill = location)) + 
  geom_jitter(position = position_nudge(x = -0.2, y = 0), alpha = 0.1) +
  geom_boxplot(width = 0.2, outlier.shape = NA, alpha = 0.5) +
  geom_flat_violin(position = position_nudge(x = 0.2, y = 0), 
                   stat = "ydensity",
                   alpha = 0.8, scale = "count") +
  stat_summary(fun = "mean", colour = "red", size = 1, geom = "point") +
  scale_color_viridis_d(option = "H") + 
  scale_fill_viridis_d(option = "H") + 
  theme_test() +
  facet_grid(month ~ crop, scales = "free") +
  coord_flip() +
  labs(x = NULL, y = NULL) +
  theme(legend.position = "none",
        strip.text = element_markdown(face = "bold")) -> fg4
```

```{r}
data1 %>% 
  mutate(location = str_to_title(location)) %>% 
  filter(crop == "fallow") %>% 
  filter(!is.na(height)) %>% 
  ggplot(aes(x = fct_reorder(location, height), y = height,
             color = location, 
             fill = location)) + 
  geom_jitter(position = position_nudge(x = -0.2, y = 0), alpha = 0.1) +
  geom_boxplot(width = 0.2, outlier.shape = NA, alpha = 0.5) +
  geom_flat_violin(position = position_nudge(x = 0.2, y = 0), 
                   stat = "ydensity",
                   alpha = 0.8, scale = "count") +
  stat_summary(fun = "mean", colour = "red", size = 1, geom = "point") +
  scale_color_viridis_d(option = "H") + 
  scale_fill_viridis_d(option = "H") + 
  theme_test() +
  facet_grid(month ~ crop, scales = "free") +
  coord_flip() +
  labs(x = NULL, y = "Height (cm)") +
  theme(legend.position = "none",
        strip.text = element_markdown(face = "bold")) -> fg5
```

```{r}
data1 %>% 
  mutate(location = str_to_title(location)) %>% 
  filter(crop == "soybean") %>% 
  filter(!is.na(height)) %>% 
  ggplot(aes(x = fct_reorder(location, height), y = height,
             color = location, 
             fill = location)) + 
  geom_jitter(position = position_nudge(x = -0.2, y = 0), alpha = 0.1) +
  geom_boxplot(width = 0.2, outlier.shape = NA, alpha = 0.5) +
  geom_flat_violin(position = position_nudge(x = 0.2, y = 0), 
                   stat = "ydensity",
                   alpha = 0.8, scale = "count") +
  stat_summary(fun = "mean", colour = "red", size = 1, geom = "point") +
  scale_color_viridis_d(option = "H") + 
  scale_fill_viridis_d(option = "H") + 
  theme_test() +
  facet_grid(month ~ crop, scales = "free") +
  coord_flip() +
  labs(x = NULL, y = NULL) +
  theme(legend.position = "none",
        strip.text = element_markdown(face = "bold")) -> fg6
```

```{r}
f5 <- fg4 | fg5 | fg6 +
  plot_annotation(
  title = NULL) 
  ggsave("height.png", width = 9, height = 5, dpi = 600, f5)
```
